Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-25 sections/tensors.tex
done with tensors

%Future
%work might involve supporting random access construction for additional
%structures, especially those with asymptotic benefits such as SparseRLE, with
%the understanding that we can use more general structures as intermediates to
%convert to more specialized structures later.

%This leave

>>>>

\begin{enumerate}
\item[SparseHash]
    The sparse hash format uses a hash table to store the locations of nonzeros,
    and sorts the unique indices for iteration during the freeze phase. This
    allows for efficient random access, but not incremental construction, as the
    freeze phase runs in time proportional to the number of nonzeros in the
    entire level.
    \begin{enumerate}
        \item[$idx$] A vector of nonzero indices in the level
        \item[$ptr$] A vector of delimiters such that $idx[ptr[p]:ptr[p+1] - 1]$ is the set of nonzero indices in the subfiber at position $p$.
        \item[$tbl$] A hash table used for construction of the level.
    \end{enumerate}
\item[SparseBytemap]
    The SparseBytemap format uses a bytemap to store which locations have been
    written to. Unlike the SparseHash format, the bytemap assembles the entire
    space of possible subfibers. This accelerates random access in the format,
    but requires a high memory overhead. Because we don't want to reallocate all
    of the memory in each iteration, the declaration of this format instead
    re-assembles only the dirty locations in the tensor. This format is
    analogous to the default workspace format used by TACO.
    \begin{enumerate}
        \item[$idx$] A vector of nonzero indices in the level
        \item[$ptr$] A vector of delimiters such that $idx[ptr[p]:ptr[p+1] - 1]$ is the set of nonzero indices in the subfiber at position $p$.
        \item[$tbl$] A dense array of booleans used to mark dirty locations in the tensor.
    \end{enumerate}
\end{enumerate}

As future work, we also recommend the implementation of a tree-based format, as
this would enable incremental construction. Currently, the cost of freezing and
thawing is usually proportional to the number of stored fibers, so an operation
that sets a single value in a tensor would be prohibitively expensive (i.e.
$A[3, 4] = 3.14$). We would also recommend supporting SparseRLE as an
intermediate randomly accessible structure, because (unlike blocks or
singletons), runs have asymptotic benefits. However, these cases were not
necessary for our case studies.
